Outline

### 2017-07-21 Outline.Rmd
modified formatting

###Educational problem solved
+ Interactive platform to learn coding, with built in assistance and checks

###Infrastructure provided to assist statistics educators
+ Take advantage of existing premium courses or build your own community course

###Pedagogical context
+ How technology is meant to be used - can be used as traditional homework assignment, in the classroom during lab periods, as pre-class assignments for flipped classrooms, even as a  test or assessment tools??
+ Intendend users - novice through advanced programming students will benefit, any college educator can access or contribute
+ Skills or concepts learned - focus is on coding in R to obtain statistical results, with some interpretation

###High level description of technology
+ features of the design

###Comparison and contrast with competing technologies

###Explain why technology is innovative
+ Coding lesson / instructions are juxtaposed with practice window

###How to Create a DataCamp Community Course
+ What is needed to get started:  DataCamp account (verified instructor), GitHub
+ How to start building (including with collaborators)
+ Examples of DataCamp code for building different types of modules

>>>>

### Educational problem solved
+ Interactive platform to learn coding, with built in assistance and checks

### Infrastructure provided to assist statistics educators
+ Take advantage of existing premium courses or build your own community course

### Pedagogical context
+ How technology is meant to be used - can be used as traditional homework assignment, in the classroom during lab periods, as pre-class assignments for flipped classrooms, even as a  test or assessment tools??
+ Intendend users - novice through advanced programming students will benefit, any college educator can access or contribute
+ Skills or concepts learned - focus is on coding in R to obtain statistical results, with some interpretation

### High level description of technology
+ features of the design

### Comparison and contrast with competing technologies

### Explain why technology is innovative
+ Coding lesson / instructions are juxtaposed with practice window

### How to Create a DataCamp Community Course
+ What is needed to get started:  DataCamp account (verified instructor), GitHub
+ How to start building (including with collaborators)
+ Examples of DataCamp code for building different types of modules
